\documentclass[aps,letterpaper,11pt]{revtex4}
\usepackage{graphicx} % For images
\usepackage{float}    % For tables and other floats
\usepackage{verbatim} % For comments and other
\usepackage{amssymb}  % For more math
\usepackage{fullpage} % Set margins and place page numbers at bottom center
\usepackage{listings} % For source code
\usepackage[usenames,dvipsnames]{color} % For colors and names
\usepackage[pdftex]{hyperref}           % For hyperlinks and indexing the PDF
\usepackage{pdfpages}
\usepackage{subfig}
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{color}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
% Custom colors
\definecolor{deepblue}{rgb}{0,0,0.5}
\definecolor{deepred}{rgb}{0.6,0,0}
\definecolor{deepgreen}{rgb}{0,0.5,0}

 \lstset{
  tabsize=4,
  language=C++,
  captionpos=b,
  tabsize=3,
  numberstyle=\tiny,
  numbersep=5pt,
  breaklines=true,
  showstringspaces=false,
  basicstyle=\footnotesize,
%  identifierstyle=\color{magenta},
  keywordstyle=\color[rgb]{0,0,1},
  commentstyle=\color{deepgreen},
  stringstyle=\color{deepred}
  }
  
\hypersetup{ % play with the different link colors here
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=blue % set to black to prevent printing blue links
}

\newcommand{\labno}{Meeting n. 4}
\newcommand{\labtitle}{Software Engineering Project}
\newcommand{\authorname}{Antoine Merlet}
\newcommand{\professor}{Dr. Yohan Fougerolle, Dr. Cansen Jiang, Dr. David Strubel}


\begin{document}  
\begin{titlepage}
\begin{center}
{\LARGE \textsc{\labno:} \\ \vspace{4pt}}
{\Large \textsc{\labtitle} \\ \vspace{4pt}} 
\rule[13pt]{\textwidth}{1pt} \\ \vspace{150pt}
{\large By: \authorname \\ \vspace{10pt}
Professor: \professor \\ \vspace{10pt}
\today}
\end{center}




\end{titlepage}% END TITLE PAGE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\tableofcontents
\newpage

This fourth meeting was held on 4, December 2017, with all the group members.

\section{Achieved goals}

Here is the state of the project at the time of the meeting:

\begin{itemize}
\item Marcio: Managed to acquire data vertically. Therefore, PC are now rotated by 90°. Make options for camera orientation. Saving as PCD needs to be tried with kinect (header problem).
\item Mladen: Studied GUI, defined the main features to be implemented.
\item Gulnur: Need to fix PC show. Implemented ICP KD tree on matlab. better than ICP for speed and accuracy. One more articlehas been found and looks interesting. Allthe current projects are using the same filtering methods (passthrough, laplacian). Prototyping on matlab.
\item Antoine: Started to do the software design, need the other parts to continue.
\end{itemize}

Here are the goals to reach for next week:

\begin{itemize}
\item Gulnur: Analyse new paper, prototype in matlab, read about filtering, report on PCL function usages
\item Marcio: Try to save pcd from kinect acquisition, work with antoine regarding the IO design.
\item Mladen: Final design of the GUI, 
\item Antoine: Continue specifying the UML, work with team to determine relevant parts.
\end{itemize}


\end{document} % DONE WITH DOCUMENT!

