\documentclass[aps,letterpaper,11pt]{revtex4}
\usepackage{graphicx} % For images
\usepackage{float}    % For tables and other floats
\usepackage{verbatim} % For comments and other
\usepackage{amssymb}  % For more math
\usepackage{fullpage} % Set margins and place page numbers at bottom center
\usepackage{listings} % For source code
\usepackage[usenames,dvipsnames]{color} % For colors and names
\usepackage[pdftex]{hyperref}           % For hyperlinks and indexing the PDF
\usepackage{pdfpages}
\usepackage{subfig}
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{color}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
% Custom colors
\definecolor{deepblue}{rgb}{0,0,0.5}
\definecolor{deepred}{rgb}{0.6,0,0}
\definecolor{deepgreen}{rgb}{0,0.5,0}

 \lstset{
  tabsize=4,
  language=C++,
  captionpos=b,
  tabsize=3,
  numberstyle=\tiny,
  numbersep=5pt,
  breaklines=true,
  showstringspaces=false,
  basicstyle=\footnotesize,
%  identifierstyle=\color{magenta},
  keywordstyle=\color[rgb]{0,0,1},
  commentstyle=\color{deepgreen},
  stringstyle=\color{deepred}
  }
  
\hypersetup{ % play with the different link colors here
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=blue % set to black to prevent printing blue links
}

\newcommand{\labno}{Meeting n. 3}
\newcommand{\labtitle}{Software Engineering Project}
\newcommand{\authorname}{Antoine Merlet}
\newcommand{\professor}{Dr. Yohan Fougerolle, Dr. Cansen Jiang, Dr. David Strubel}


\begin{document}  
\begin{titlepage}
\begin{center}
{\LARGE \textsc{\labno:} \\ \vspace{4pt}}
{\Large \textsc{\labtitle} \\ \vspace{4pt}} 
\rule[13pt]{\textwidth}{1pt} \\ \vspace{150pt}
{\large By: \authorname \\ \vspace{10pt}
Professor: \professor \\ \vspace{10pt}
\today}
\end{center}




\end{titlepage}% END TITLE PAGE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

This third meeting was held on 27, November 2017, with all the group members.

\section{Achieved goals}

Here is the state of the project at the time of the meeting:

\begin{itemize}
\item Previous projects are running on each member computer
\item All the previous report were read
\item Marcio: Managed to interface the Kinect and his computer. Data acquisition can be performed with the Kinect SDK or using the project 3D-Korn 
\item Mladen: Started the study of the previous groups GUI. 3D-Korn is best overall, and the-scanner has interesting setting possibilities for ICP.
\item Gulnur: Reading papers for registration process, mostly for ICP. Attention is currently given to ICP based on Kd-tree, with complexity reduction against usual ICP. Looking into GPA+ICP and Geometric features + ICP
\item Antoine: Started reviewing the code. Selected 3D-Korn and the-scanner are selected for code inspiration/improvement.
\end{itemize}

Here are the goals to reach for next week:

\begin{itemize}
\item For Marcio, Mladen and Antoine: Finish all review and design by this week, start coding next week.
\item for Gulnur: Continue readingfor ICP improvement, "prototype" on matlab to see efficiency.
\item Marci: try to fix PCD saving, try vertical acquisition.
\item Mladen: Learn about slots and GUI building.
\item Antoine: Start to extract good functions from previous code, produce UML class diagram.
\end{itemize}


\end{document} % DONE WITH DOCUMENT!

